A Triple Origin for Twin Blue Stragglers in Compact Binaries

### 2018-12-06 apjl.tex
Add files via upload

>>>>

Finally, in future work, we intend to explore the implications of the mechanism proposed here for other types of stellar triples.  The results highlight that specific theoretical predictions can often be made.  For example, if two white dwarfs form the inner compact binary, than circumbinary accretion could push one of them above the Chandrasekhar mass limit.  Upon explosion, its WD companion would be ejected at roughly the orbital velocity at the time of explosion, producing a hypervelocity WD.  This predicts hot hypervelocity WDs with masses very close to the Chandrasekhar mass limit for this scenario.  Similarly, if the two WDs are replaced with two neutron stars (NSs), then one NS will likely accrete to surpass the critical supernova limit, upon which time it explodes to become a black hole and receives a strong natal kick.  The NS companion would have a very comparable mass to the newly formed black hole progenitor at the time of explosion, and could potentially be used to constrain the maximum NS mass.
